Supplementary Appendix

### 2025-02-18 supplementary_appendix.qmd
There is magic in this world, I do not understand it!

Prisma Eco-Evo Checklist @odea2021
:::

::: {#figsupp-string}
The search was conducted twice, the first time on 07.09.2022 and then repeated on 12.08.2024 to ensure it was the most up to date and did not miss any additional articles on the topic that were published meanwhile. For both the searches, we did not use any time limitation i.e. it included all the published literature till that given date. We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.

{{< include search_string.txt >}}
:::

>>>>

Prisma Eco-Evo Checklist according to @odea2021
:::

::: {#figsupp-string}
The search was conducted twice, the first time on 07.09.2022 and then repeated on 12.08.2024 to ensure it was the most up to date and did not miss any additional articles on the topic that were published meanwhile. For both the searches, we did not use any time limitation i.e. it included all the published literature till that given date. We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.\
\
Search string for the Web of Science Core Collection\
Databases used in the search included\
-Science Citation Index Expanded (SCI-EXPANDED) \[1900-present\]\
-Social Sciences Citation Index (SSCI) \[1900-present\]\
-Arts & Humanities Citation Index (AHCI) \[1975 - present\]\
-Conference Proceedings Citation Index - Science (CPCI-S) \[1991 - present\]\
-Conference Proceedings Citation Index - Social Science & Humanities (CPCI-SSH) \[1991 - present\]\
-Emerging Sources Citation Index (ESCI) \[2017- present\]\
\
We used advance search option and Title (TI), Abstract (AB) and Author Keywords (AK) to conduct our systematic search using the following string\
\
